**Density Dependence**

### 2023-03-07 Rmd/report mac.Rmd
Updated report.R and report mac

**L. Kell, M.A. Pastoors**

@@

Commissioned by: University of Copenhagen (Henrik Sparholt)

@@

**Figure X4** summaries the yields and SSBs obtained for each Operating Model under the correct and misspecified form of density dependence.

@@

-   The impact of including density dependence: major impact on reference points. Especially $F_{MSY}$ is much higher when including DD. However, the expected yields in equilibrium conditions are expected to be very similar. The main difference is in the initial step from the current $F_{MSY}$ to any new $F_{MSY}$ that would include DD, as the higher $F_{MSY}$ would be applied to a stock that is estimated without DD.
-   The impact of ignoring density dependence
-   The impact of assuming density-dependence incorrectly
-   Robustness of the current ICES framework

@@

All data and results are available on DropBox (<https://www.dropbox.com/sh/k87x074xqw7sgae/AAAmF980iR2n24wTkqhOhnpfa?dl=0>)

@@

Ignoring density dependent processes when they would be happening is expected to lead to ...

The impact of assuming the wrong type of density-dependence processes, i.e. applying the reference points from the one density dependent operating model to a simulation with other density dependent processes, could lead to ....

@@

@@

<!-- Annex 1: OM conditioning                                                                           -->

# Annex 1: OM conditioning

<!-- Annex 2: Density dependent processes                                                                           -->

# Annex 2: Density dependent processes

>>>>

**`r ifelse(mystk=="mac", "M.A. Pastoors & L.T. Kell", "L.T. Kell & M.A. Pastoors")`**

@@

Version: 1.0 (draft)

&nbsp;

**Commissioned by:**

Henrik Sparholt

University of Copenhagen

Globe Institute

Center for Macroecology Evolution and Climate

Universitetsparken 15, 3rd floor, room 339

2100 Copenhagen Ø

Denmark

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

```{r, echo=FALSE, out.width = "300px", fig.align="left", message=FALSE, warning=FALSE, cache=FALSE}

if(mystk=="mac") {
  knitr::include_graphics("../MPFF Seaplusplus.png")
} else {
  knitr::include_graphics("../Seaplusplus MPFF.png")
}

@@

**Figure X4** summarizes the yields and SSBs obtained for each Operating Model under the correct and mis-specified form of density dependence.

@@

The impact of including density dependence: major impact on reference points. Especially $F_{MSY}$ is much higher when including DD. However, the expected yields in equilibrium conditions are expected to be very similar. The main difference is in the initial step from the current $F_{MSY}$ to any new $F_{MSY}$ that would include DD, as the higher $F_{MSY}$ would be applied to a stock that is estimated without DD.

REMOVE 
[ -   The impact of ignoring density dependence ]
[ -   The impact of assuming density-dependence incorrectly ]
[ -   Robustness of the current ICES framework ]

@@

All data and results are available on a dedicated DropBox folder.

@@

REMOVE

[ Ignoring density dependent processes when they would be happening is expected to lead to ... ]

[ The impact of assuming the wrong type of density-dependence processes, i.e. applying the reference points from the one density dependent operating model to a simulation with other density dependent processes, could lead to .... ]

@@

This work was funded under a consultancy agreement between the University of Copenhagen and `r ifelse(mystk=="mac", "Martin Pastoors F&F", "Sea++")` as part of the project “117957 Fmsy-project for six high profile fish stocks”. The current work focused on `r mystkname` and was carried out in the months of January-March 2023. A similar project was carried out for `r ifelse(mystk=="mac", "Blue whiting", mystkname)` by `r ifelse(mystk=="mac", "Sea++", "Martin Pastoors F&F")`. Both projects were carried in close coordination between Sea++ and Martin Pastoors F&F.

@@
